Make any stupid plot you want

### 2020-12-16 draft/sections/math.tex
revised render while working out nu

@@

\begin{equation}
\tau(k) =(k, (r: \textrm{Temp}\rightarrow temp, r: \textrm{Time}\rightarrow time))\\
temp \in [temp_{min}, temp_{max}], time \in [time_{min}, time_{max}])
\end{equation}

@@

where $\rho: H \rightarrow S$ is mapping from a mathematical encoding of the image to a region $xy$ on the screen that the renderer then maps to pixel space.

For a physical screen display, the fiber $D$ encodes position and color of the visual elements as $\mathbb{R}^{7} = \{X, Y, Z, R, G, B, A\}$, where the patch $xy$ is a region in $H$ that we query into $S$ to get values that we integrate into an $\{r, g, b\}$ value. In the case of 2D screens, the predisplay space is a trivial fiber bundle $H=\mathbb{R}^{7}\times S$.

To draw an image, a region  $H$ is inverse mapped into a region $s \in S$ where $s$ is the inverse mapping from pixel to region on $s = \rho^{-1}_XY(xy)$ such that the rest of the fields in $\mathbb{R}^{7}$ are then integrated over $s$ to yield the remaining fields in $p$
\begin{align}
    R(p) &= \oint_s \rho_R(s)ds^{2}\\
    G(p) &= \oint_s \rho_G(s)ds^{2}\\
    B(p) &= \oint_s \rho_B(s)ds^{2}
\end{align}

@@

The aesthetic property mapper $\Xi=Q\circ\nu$  builds $\rho$ functions via a function $Q$ that compose $\nu_{param}( \xi^*\tau)$ functions that map data in some field $c$ to a subset of $D$, such as x, or RGB. These $\rho$ functions are then mapped back into $S$ to provide the values for the region in $H$. $Q$ is analogous to a visualization type such as scatter or line plot, and $\nu$ to aesthetic parameters such as line color or marker shape \cite{bertinIIPropertiesGraphic2011, munznerMarksChannels}.

\begin{equation}
     \rho(u, v) = Q(\nu_{param_{n}}(\tau_{c_0}), \ldots \nu_{param_{n}}(\tau_{c_n}))(u,v)
    \label{eq:Q}
\end{equation}

$Q$ composites $\nu$ functions because multiple parameters can target the same field in $D$, for example $\nu_{ypos}$ and $\nu_{linewidth}$ together determine the output of the $\rho_y$ y position of a line on screen.

@@

Each point $s$ in the display space $H$, the mark it belongs to can be found by mapping $s$ back to $K$ via the lookup on S

@@

\subsubsection{Channels}
For the aesthetic mapping function $\nu$ to faithfully transform the data in $\xi^*\tau$, the $\nu$ and $\tau$ must be symmetrical under all transformations such that
\begin{equation}
    \nu_{param}(\tau_{})
\end{equation}

>>>>

\begin{multline}
\tau(k) =(k, (r: \textrm{Temp}\rightarrow temp, r: \textrm{Time}\rightarrow time))\\
temp \in [temp_{min}, temp_{max}], time \in [time_{min}, time_{max}])
\end{multline}

@@

@@

where $\rho: S \rightarrow H$ is mapping from a region $s$ on a mathematical encoding of the image to a region $xy$ on the screen that the renderer then maps to pixel space. For a physical screen display, the predisplay space is a trivial fiber bundle $H=\mathbb{R}^{7}\times S$ such that $\rho$ is
\begin{equation}
    \rho(s)  = \{x, y, z, g, b, a\}
    \label{eq:rho}
\end{equation}

To draw an image, a region, $H$ is inverse mapped into a region $s \in S$ where
\begin{equation}
s = \rho^{-1}_{XY}(xy)
\end{equation}
such that the rest of the fields in $\mathbb{R}^{7}$ are then integrated over $s$ to yield the remaining fields in $p$

\begin{align}
    R(p) &= \oint_s \rho_R(s)ds^{2}\\
    G(p) &= \oint_s \rho_G(s)ds^{2}\\
    B(p) &= \oint_s \rho_B(s)ds^{2}
\end{align}

@@

\subsubsection{Channels}

The visualization specification function $\Xi=Q\circ\nu$  builds $\rho$ functions via a function $Q$ that compose $\nu_{param}$ visual characteristic mappers
\begin{equation}
    \nu_{param}(\tau_{param}) = \mu_{param}
\end{equation}
where $\tau_{param}$ is a field in $\tau$ bound to the paremeter and $\mu_param$ is an intermediate visual representation such that $\nu_shape(\tau_shape)$ returns a $\mu_shape$ function that returns a shape for each $k$. $Q$ then composites the $\nu$ functions to build $\rho$ as described in equation~\ref{eq:rho}

\begin{equation}
    Q(\mu_{param_0}, \ldots, \mu_{param_n}(s) = \rho(s)
    \label{eq:Q}
\end{equation}

$Q$ is analogous to a visualization type such as scatter or line plot, and $\nu$ to aesthetic parameters such as line color or marker shape \cite{bertinIIPropertiesGraphic2011, munznerMarksChannels} and composites the $\nu$ mappings into $\rho$ functions as

@@

Each point $s$ in the display space $H$, the mark it belongs to can be found by mapping $s$ back to $K$ via the lookup on $S$

@@
